\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{parskip}
%\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}

%opening
\author{Simon Cholewa}
\title{7. Tool Supported Data Cleaning}

\hyphenation{
	Mo-tor-ü-ber-wach-ung 
}


\begin{document}

\maketitle

\section{dsm-beuth-edl-demodata-dirty}

\textit{Clean the \hyperref{https://github.com/edlich/eternalrepo/blob/master/DS-WAHLFACH/dsm-beuth-edl-demodata-dirty.csv}{}{}{dsm-beuth-edl-demodata-dirty.csv} mini csv from the first exercise with Trifacta Wrangler (if you have no cloud access use the download version).}



\textit{Not the red bars that give you instant feedback (on big datasets) where errors could be!}

\textit{Create a recipie to clean the data as good as you can (it must not be a general script). Try to upload only one file (e.g. with screenshots and the end result). (10 points)}


\section{15 Years of Power Outages}

\textit{Load\ the\ Grid\_Disruption\_00\_14\_standardized -}\\ \textit{Grid\_Disruption\_00\_14\_standardized.csv Dataset from Kaggle:
\hyperref{https://www.kaggle.com/autunno/15-years-of-power-outages}{}{}{15 YEARS OF POWER OUTAGES}.}

\textit{Where are errors here? => Describe some errors and a possible cleaning in text.}

\textit{How would you clean this file? (5 Points) => Try to create some cleaning recipies in Trifacta (e.g. 3) The idea here is that I can see, you have dug into this system! You must not clean all errors.}


\end{document}
